Interactive results review

### 2024-08-05 nbs/guides/interactive/interactive.qmd
docs(nbs): generate phase portraits from custom gene list
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

@@

>>>>

#### Gene selection summary plot

@@

#### Phase portraits from custom gene list

One of the primary applications of interactive review may be to explore
specific genes of interest. Here we generate phase portraits for a randomly
selected list of genes.

```{python}
# | label: generate-phase-portraits-from-gene-list
# | output: false
from pyrovelocity.plots import rainbowplot

rainbowplot(
    volcano_data=volcano_data,
    adata=adata,
    posterior_samples=posterior_samples,
    genes=["1839", "927", "15"],
    data=["st", "ut"],
    basis=vector_field_basis,
    cell_state=cell_state,
    save_plot=True,
    rainbow_plot_path="gene_selection_rainbow_plot.pdf",
)
```

```{python}
# | label: show-phase-portraits-from-gene-list
# | code-fold: true
# | output: true
display(Image(filename=f"gene_selection_rainbow_plot.pdf.png"))
```
